---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# packageName- pigment

<!-- badges: start -->
<!-- badges: end -->

Pigment is a substance, which leaves a stain/color when mixed. The goal of **pigment** is to provide access to some regular day to day colors. The package pigment has one palette- **stain** which includes colors like yellow, shades of brown like skin, wood and tan, along with 2 different colors like teal and dark pink. 

## Installation

The development version of *pigment* with palette *stain* can be installed in the following way. The result is a set to return corresponding hexcode of the colour name to the ggplot. Configuration can be confirmed by using seecol("colossal_colours", col_bg = "grey90", col_brd = "black") command.

GitHub_repo_url("https://github.com/etc5523-2021/r-package-takehome-ratulwadhwa.git")

**steps to install pigment package:**

* install.packages("devtools")

* library(devtools)

* dev_mode(on=T)

* install_github("etc5523-2021/r-package-takehome-ratulwadhwa")

* when finished do: dev_mode(on=F)

* Use install.packages("pigment") command to install the package.

* load library- library(pigment)


```{r install, eval = FALSE}
install.packages("devtools")
remotes::install_github("etc5523-2021/r-package-takehome-ratulwadhwa")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(pigment)
## basic example code
```

```{r warning=FALSE, message=FALSE}
library(pigment)
library(tidyverse)
library(ggplot2)
library(palmerpenguins)

ggplot(penguins, aes(body_mass_g, flipper_length_mm, fill = species)) +
  geom_col() +
pigment::scale_fill_stain_d()+
  labs(title = "Example of Color palette: shows first three colors of the palette")
```

```{r warning=FALSE, message=FALSE}
ggplot(penguins, aes(bill_length_mm, bill_depth_mm, colour = body_mass_g)) +
  geom_point() +
   theme_bw()+
pigment::scale_colour_stain_seq_c("wood")+
  labs(title = "Example of Continuous Color: wood")

```

