---
title: "Vignette_File"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette_File}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(pigment)
library(tidyverse)
library(ggplot2)
library(palmerpenguins)
```

**The below plot gives an overview of Stain palette, and the colours that are in it**

```{r}
library(unikn)
names("stain_colours")
```

  "lemon"     = "#FCF404",
  "pink"      = "#EC3C7C",
  "teal"      = "#057277",
  "tan"       = "#9C8877",
  "skin"      = "#C9A58C",
  "wood"      = "#52292A"
  
The above list shows the 6 different colors with their hex-code which are present in the palette **stain**, the colors used in the palette are the few day to day ordinary colors.

```{r}
library(unikn)
my_pair <- seecol(stain_colours, n = 6)

dat <- matrix(sample(5:10, size = 10, replace = TRUE), ncol = 3)
# Plot in my_pair colors:
barplot(dat, beside = TRUE, col = my_pair)
```

Visual representation of the Color palette.

**Example of Discrete Color**

```{r warning=FALSE, message=FALSE}
ggplot(penguins, aes(year, bill_length_mm, color = species)) +
  geom_bar(stat="identity", size=.3) +
pigment::scale_color_stain_d()+
  theme_bw()+
  labs(title = "Example of Discrete Color")
```

**Example of Continuous Color**

```{r warning=FALSE, message=FALSE}
ggplot(penguins, aes(bill_length_mm, bill_depth_mm, colour = body_mass_g)) +
  geom_point() +
   theme_bw()+
pigment::scale_colour_stain_seq_c("wood")+
  labs(title = "Example of Continuous Color")

```

**Example of Discrete Fill**

```{r warning=FALSE, message=FALSE}
ggplot(penguins, aes(year, fill = species)) +
  geom_bar() +
   theme_bw()+
pigment::scale_fill_stain_d(direction = -1)+
  labs(title = "Example of Discrete Fill")
```
